Assignment 4

### 2015-03-10 rmtw/a4/latex8.tex
learn to write messages john

When looking at the results of the study, UC appears to find many more class A and class B faults than CL, however, CL finds more class B faults. However, on average, the CL reviews found more faults overall and as such could be considered more effective than UC. This, coupled with the rejection of the H\texsubscript{Fault} null hypothesis, provides ample evidence that the review techniques do differ in which faults they are finding. A suggestion for a follow up study would be to determine exactly  and why one inspection process finds them over the other.

\begin{table}
	\centering
	\begin{tabular}[Ht]{| l | l | l | l | l | l | l |}
	\hline
	 & A Faults & B Faults & C Faults & Mean & Median & Detection Rate\\
	\hline
	UC & 36 & 40 & 35 & 4.61 & 3.5 & 0.12 \\
	\hline
	CL & 31 & 47 & 28 & 5.48 & 5 & 0.14 \\
	\hline
	\end{tabular}
	\caption{Results Summary}
\end{table}

>>>>

When looking at the results of the study, UC appears to find many more class A and class B faults than CL, however, CL finds more class B faults. However, on average, the CL reviews found more faults overall and as such could be considered more effective than UC. This, coupled with the rejection of the H\textsubscript{Fault} null hypothesis, provides ample evidence that the review techniques do differ in which faults they are finding. A suggestion for a follow up study would be to determine exactly  and why one inspection process finds them over the other.

\begin{table}
	\centering
	\begin{tabular}[Ht]{|l|l|l|}
	\hline
	& UC & CL \\
	\hline
	Mean(Total faults found) & 4.61 & 5.48 \\
	\hline
	Median(Total faults found) & 3.5 & 5.0 \\
	\hline
	Detection Rate & 0.12 & 0.14 \\
	\hline
	A Faults & 36 & 31 \\
	\hline
	B Faults & 40 & 47 \\
	\hline
	C Faults & 35 & 20 \\
	\hline
	\end{tabular}
	\caption{Results Summary}
\end{table}
